
Question 1: 
Least Squares Estimate, of the Slope and the Intercept?
- Slope 38.91
- Intercept: 3.04

Standard Errors?
Check standard errors using R to calculate Mean and ??? Sxx

- 

```{r}
model1 <- lsfit(ChickWeight$Time, ChickWeight$weight)

moddiag <- ls.diag(model1)
names(moddiag)
moddiag$std.err

```
Check standard errors using R to calculate x and Sxx??
- Intercept 3.04
- X = 0.24

Least Squares Estimate, of the Slope and the Intercept?
- Slope 8.80
- Intercept: 27.46

Standard Errors?
- Residual standard error 38.91
- STE Intercept: 3.04
- STE Time 0.24


```{r}
model2 <- lm(weight ~ Time, data=ChickWeight)
summary(model2)
```

Question 2
Superimpose the regresison line

```{r}
model1 <- lsfit(ChickWeight$Time, ChickWeight$weight)
plot(ChickWeight$Time, ChickWeight$weight)
abline(model1$coef)
```
Question 2
- What is the weight on day 25 and 30?
```{r}
27.46+8.08*25
27.46+8.08*30
```

Answer, 229.46 and 269.86 weight units

Question 3

Find the centroid of the dataset

```{r}
mean(ChickWeight$Time)
mean(ChickWeight$weight)
```

X=10.72
Y=121.80

```{r}
model2 <- lm(weight ~ Time, data=ChickWeight)
summary(model2)

fit1 <- fitted(model2)
res1 <- residuals(model2)
plot(fit1, res1)
```
Does this satisfy conditions for linear model?
- The criteria of heteroskedasticity holds are uniformly distributed across each respective value.

Second Question
#1 Show by derivation that the hat matrix H and the matrix I - H are projections.

See separate jpeg

#2. Create a vector called spd
```{r}
View(cars)
```

```{r}
spd <- c(cars$speed)
```

#Create a design matrix X

Don't know wheter to use =25 or 50

```{r}
X = matrix(spd, nrow=25, ncol=2, byrow=T)
X[1:25,1]=1
View(X)
```

#3. Hat matrix

H = X(X^tX)^(-1)X^t

solv(A) Inverse of A where A is a square matrix.
```{r}
H = X%*%(solve((t(X)%*%X)))%*%t(X)
diag(H)
```

```{r}
h = H%*%H
h
```

```{r}
H
```

h=H 

Answer: these seem to correspond 

#4. Matrix calculation to find LSQE

```{r}
x = matrix(c(cars$speed), nrow=25, ncol=2, byrow=T)
y = matrix(c(cars$dist), nrow=25, ncol=2, byrow=T)

S = solve(t(x)%*%x)%*%t(x)%*%y
S
```
These results does not correspond to those of the lm() function and thus there is something the reasoning and the code
```{r}
model2 <- lm(cars$dist ~ cars$speed)
summary(model2)
```


